---
title: "Markdown is the best"
author: "Erin Walsh"
date: "16 January 2019"
output: html_document
---

This is my first Markdown document.

```{r echo=FALSE, warning=FALSE, message=FALSE, results='hide'}

# Example chunk of code
# E. Walsh
# Last edited: 16/01/2019

## Packages
  library(psych) # psych_1.5.8 for descriptives

## Data
      
  # Sensor data from house 10:25 PM to 8:02 AM 15/1/2019
    # Timestamp is ISO8601 formatted, samples every ~ 5 minutes.
    # Temperature is in Centigrade.
    # Humidity is in %.
      sensornet_dat<-read.csv("sensornet-01__16_1_2019.csv")     

## Functions
  # Takes two numbers, returns their sum multiplied by the first input.
    another_simple_function<-function(number,anothernumber){added<-number + anothernumber
                                                        multiplied<-added * number
                                                        return(multiplied)}
## Scripts
  # Adds simple_function() and nested_function()
    source("example_script_containing_functions.R")

    
## Analysis
    
    # Loop over temperature to perform some operation
      temperature_transformed<-vector()
      for(i in 1:nrow(sensornet_dat)){
                      temperature_transformed[i]<-nested_function(2,sensornet_dat$temperature[i])}
      
      temperature_transformed
    
      describe(temperature_transformed)
      
      describe(sensornet_dat$temperature)
      
      mean_temp_before<-describe(sensornet_dat$temperature)$mean
    
      mean_temp_after<-describe(temperature_transformed)$mean
      
      mean_temp_before
      
      mean_temp_after
      
    
      library(stargazer) # Normally this would go up the top but just putting it here for demonstration
      
      linear_model<-glm(humidity ~ temperature, data=sensornet_dat)
      
      summary(linear_model)
      

```



One night (15th-16th January 2019) we measured the temperature and humidity in our house every five minutes or so, overnight. The average overnight temperature was `r round(mean_temp_before,2)` degrees.

Then I brought the data into R and did some nefarious things with loops and functions.

Now it appears the average overnight temperature was `r round(mean_temp_after,2)` degrees. Deadly.

Fine, but what is the actual relationship between temperature and humidity? A table can help us find out.

```{r echo=FALSE, results='asis'}
      
stargazer(linear_model, type="html")
      
      
```
