---
title: "Worked Markdown Example"
author: "E. Walsh"
date: "14 March 2019"
output: html_document
---

<script type="text/javascript" language="JavaScript"><!--
function HideContent(d) {
document.getElementById(d).style.display = "none";
}
function ShowContent(d) {
document.getElementById(d).style.display = "block";
}
function ReverseDisplay(d) {
if(document.getElementById(d).style.display == "none") { document.getElementById(d).style.display = "block"; }
else { document.getElementById(d).style.display = "none"; }
}
//--></script>



<!--Comment-->

# Heading 1
## Heading 2
### Heading 3
#### Heading 4

*italics*
**bold**
~~strikethrough~~

---

> Quote

[Link text](http://www.negaleg.com)


"Show" and "hide" here demonstrate the section folding code.

<a href="javascript:ShowContent('NAME')">Show </a>
<a href="javascript:HideContent('NAME')"> (hide)</a>
<div id="NAME" style="display:none;">

```{r sensornet_analysis}

# Remember when loading data, when you knit it considers the location of the markdown file the working directory.
# Loading datasets will throw an error and prevent compilation if the file it refers to cannot be found.

sensornet_dat<-read.csv("sensornet-01__16_1_2019.csv")     


# Variable specification for in-text reporting
average_temperature<-mean(sensornet_dat$temperature)

temp_humid_lm<-lm(temperature ~ humidity, data=sensornet_dat)

# Pull out the coefficients from the model. The second one will be the slope.
temp_humid_lm_coefficients<-coef(temp_humid_lm)

# Pull out the p values from the model. The second one will be the slope.
temp_humid_lm_pvalues<-summary(temp_humid_lm)$coefficients[,4]

# Is the association positive or negative? Test if the slope is above or below 0.

if(temp_humid_lm_coefficients[2]<0){temp_humid_association_direction<-"negatively"} else
                                   {temp_humid_association_direction<-"positively"} 

# Addition:
      # As Nic noted, a third possibility is if there is no slope at all...
      if(temp_humid_lm_coefficients[2]==0){temp_humid_association_direction<-"not"} 


# Is the association statistically significant?
if(temp_humid_lm_pvalues[2]<0.05){temp_humid_association_significance<-"significantly"} else
                                 {temp_humid_association_significance<-"not significantly"} 


# Add in synonyms!
if(temp_humid_lm_coefficients[2]<0){temp_humid_association_direction_words<-"lower"} else
                                   {temp_humid_association_direction_words<-"higher"} 

```



<a href="javascript:HideContent('NAME')">Hide</a>
</div>


The mean temperature was `r average_temperature`.


The mean temperature was `r round(average_temperature,2)`.


Temperature was `r temp_humid_association_direction` associated with humidity.


Temperature was `r temp_humid_association_significance`, `r temp_humid_association_direction` associated with humidity.


Temperature was `r temp_humid_association_significance`, `r temp_humid_association_direction` associated with humidity. Starting from `r round(temp_humid_lm_coefficients[1],2)` degrees, each additional 1% humidity was associated with `r round(temp_humid_lm_coefficients[2],2)` degrees `r temp_humid_association_direction_words` temperature.



``` {r stargazer, results='asis'}
library(stargazer)

stargazer(temp_humid_lm, type="html", star.cutoffs = c(0.05))

```


